---
title: "PMA Final Analyses"
output: 
  html_notebook:
    toc: yes
  html_document:
    toc: yes
    df_print: paged
---

# Load Libaries 
```{r}
#install.packages("car")
#install.packages("lsr")
#install.packages("MBESS")

#library(car)
#library(lsr)
#library(MBESS)
library(psych)
library(tidyverse)
library(apaTables)
```


# Load Libaries 
```{r}
PM <- read_csv("PM_Gender.csv")
```

# Recode variables 
```{r}

PM$Sex1<- 0
PM$Sex1<-ifelse(PM$Gender=="Male",-1, 1)


PM$Gender1<- 0
PM$Gender1<-ifelse(PM$Gender=="Male", 0, 
                    ifelse(PM$Gender=="Female", 1, 2))

## Explaining code : PM$Gender1<- 0 creates the new variable titled Gender1 
## PM$Gender1<-ifelse(PM$Gender ==“Male”,0 , ifelse(PM$Gender=="Female", 1, 2))) says “if the Gender is male, they will be 0, if Gender is female, they will be 1, if Gender is anything else it will be 2" 
```

```{r}
PM_Describe <- describe(PM)
PM_Describe
```


```{r}

# range of STAIS
describe(PM$STAIS)


#zero order correlation table 
desctable <- select(PM, STAIS, PP, Accuracy)

library(apaTables)

apa.cor.table(
      desctable,
      filename = "desctable.doc",
      table.number = 1,
      show.conf.interval = TRUE,
      show.sig.stars = TRUE,
      landscape = TRUE
)

apa.cor.table(desctable, filename = "desctable.doc")

library(apaTables)
corrtable <- select(PM, STAIS, STAIT, BAI , PP, N300,  Accuracy)
apa.cor.table(
      corrtable,
      filename = "corrtable2.doc",
      table.number = 2,
      show.conf.interval = TRUE,
      show.sig.stars = TRUE,
      landscape = TRUE
)
apa.cor.table(corrtable, filename = "corrtable.doc")
```
# Correlations
```{r}
model <- lm(STAIS ~ Gender1, data = PM)
summary(model)

model <- lm(STAIT ~ Gender1, data = PM)
summary(model)


model <- lm(BAI ~ Gender1, data = PM)
summary(model)


model <- lm(Accuracy ~ Gender1, data = PM)
summary(model)


model <- lm(N300 ~ Gender1, data = PM)
summary(model)


model <- lm(PP ~ Gender1, data = PM)
summary(model)
```



# Correlations: Gender and age with variables
```{r}
# Calculate Pearson correlation coefficient between (gender and accuracy)
corr1 <- cor.test(PM$Gender1, PM$Accuracy,method = "spearman")
print(corr1$estimate)
print(corr1$p.value)

# Calculate Pearson correlation coefficient between (gender and PP)
corr2 <- cor.test(PM$Gender1, PM$PP,method = "spearman")
print(corr2$estimate)
print(corr2$p.value)

# Calculate Pearson correlation coefficient between (gender and STAIS)
corr3 <- cor.test(PM$Gender1, PM$STAIS,method = "spearman")
print(corr3$estimate)
print(corr3$p.value)

# Calculate Pearson correlation coefficient between (age and accuracy)
corr4 <- cor.test(PM$Age, PM$Accuracy,method = "spearman")
print(corr4$estimate)
print(corr4$p.value)

# Calculate Pearson correlation coefficient between (age and PP)
corr5 <- cor.test(PM$Age, PM$PP,method = "spearman")
print(corr5$estimate)
print(corr5$p.value)

# Calculate Pearson correlation coefficient between (age and STAIS)
corr6 <- cor.test(PM$Age, PM$STAIS,method = "spearman")
print(corr6$estimate)
print(corr6$p.value)
```

# Regression: Anxiety controlling for Gender and Age
```{r}
## scale = standardizing the coefficients 

fit7 <- lm(scale(Accuracy) ~ scale(STAIS) + Gender1 + Age, data = PM)
summary(fit7)

fit8 <- lm(scale(PP) ~ scale(STAIS) + Gender1 + Age, data = PM)
summary(fit8)

fit9 <- lm(scale(Accuracy) ~ scale(PP) + Gender1 + Age, data = PM)
summary(fit9)
```

# Regression: Anxiety controlling for Gender and Age (N300)
```{r}
## scale = standardizing the coefficients 

fitN300a <- lm(scale(Accuracy) ~ scale(STAIS) + Gender1 + Age, data = PM)
summary(fitN300a)

fitN300b <- lm(scale(N300) ~ scale(STAIS) + Gender1 + Age, data = PM)
summary(fitN300b)

fitN300c <- lm(scale(Accuracy) ~ scale(N300) + Gender1 + Age, data = PM)
summary(fitN300c)
```


#Effect sizes (partial R-squared) for STAIS on Accuracy
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ STAIS + Age + Gender, data = PM)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

#Effect sizes (partial R-squared) for STAIS on PP
```{r}
#full linear regression model
full_model <- lm(PP ~ STAIS + Age + Gender, data = PM)
# model without the predictor
reduced_model <- lm(PP ~ Age + Gender, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

#Effect sizes (partial R-squared) for PP on Accuracy
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ PP + Age + Gender, data = PM)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for PP while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

#Effect sizes (partial R-squared) for STAIS on Accuracy
```{r}
#full linear regression model
full_model <- lm(Accuracy ~ STAIS + Age + Gender, data = PM)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
# Partial R-squared for STAIS while controlling for Age and Gender!!!
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```


Potential Scatterplots 
```{r}
#STAIS and Accuracy 
p <- ggplot(PM,aes(x=STAIS,y=Accuracy)) +
          geom_point() + geom_smooth(method=lm, se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("State Anxiety") + ylab("Prospective Memory") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="plain"))
p
#ggsave("STAIS_Accuracy", path = '/path/name/here/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)

#STAIS and PP 
p <- ggplot(PM,aes(x=STAIS,y=PP)) +
          geom_point() + geom_smooth(method=lm, se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("State Anxiety") + ylab("Prospective Positivity") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="plain"))
p
#ggsave("STAIS_PP", path = '/path/name/here/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)

#PP and Accuracy 
p <- ggplot(PM,aes(x=PP,y=Accuracy)) +
          geom_point() + geom_smooth(method=lm, se=FALSE, fullrange=TRUE, color = "black") + theme_minimal() + scale_color_grey()
p <- p + ggtitle("") + xlab("Prospective Positivity") + ylab("Prospective Memory") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20,face="plain"))
p
#ggsave("PP_Accuracy", path = '/path/name/here/', bg="white", width = 5, height = 5, device='jpeg', dpi= 700)
```


# Mediation
```{r}
# Anxiety -> PP -> Accuracy

#install.packages("mediation")
#install.packages("minqa")
#library(mediation)

model.M <- lm(PP ~ STAIS + Gender1 + Age, data = PM)
model.Y <- lm(Accuracy ~ PP + STAIS + Gender1 + Age, data =PM)
results <- mediation::mediate(model.M, model.Y, treat =  "STAIS", mediator= 'PP', 
                              boot=TRUE, sims=10000)
summary(results)


```

# Regression: Non-significant stuff
```{r}
## scale = standardizing the coefficients 

## Anxiety and PM

fitA <- lm(scale(Accuracy) ~ scale(STAIT) + Gender1 + Age, data = PM)
summary(fitA)

fitB <- lm(scale(Accuracy) ~ scale(BAI) + Gender1 + Age, data = PM)
summary(fitB)

fitC <- lm(scale(RT) ~ scale(STAIS) + Gender1 + Age, data = PM)
summary(fitC)

fitD <- lm(scale(RT) ~ scale(STAIT) + Gender1 + Age, data = PM)
summary(fitD)

fitE <- lm(scale(RT) ~ scale(BAI) + Gender1 + Age, data = PM)
summary(fitE)

## ERPs and PM

fitF <- lm(scale(RT) ~ scale(PP) + Gender1 + Age, data = PM)
summary(fitF)

fitG <- lm(scale(RT) ~ scale(N300) + Gender1 + Age, data = PM)
summary(fitG)

fitH <- lm(scale(Accuracy) ~ scale(N300) + Gender1 + Age, data = PM)
summary(fitH)

## Anxiety and ERPs

fitI <- lm(scale(PP) ~ scale(STAIT) + Gender1 + Age, data = PM)
summary(fitI)

fitJ <- lm(scale(PP) ~ scale(BAI) + Gender1 + Age, data = PM)
summary(fitJ)

fitK <- lm(scale(N300) ~ scale(STAIT) + Gender1 + Age, data = PM)
summary(fitK)

fitL <- lm(scale(N300) ~ scale(BAI) + Gender1 + Age, data = PM)
summary(fitL)

fitM <- lm(scale(N300) ~ scale(STAIS) + Gender1 + Age, data = PM)
summary(fitM)

```

# Effect sizes: Non-significant stuff
```{r}
## Anxiety and PM

#Effect sizes (partial R-squared) for TRAIT on PM
#full linear regression model
full_model <- lm(Accuracy ~ STAIT + Age + Gender1, data = PM)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender1, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)

```

```{r}
#Effect sizes (partial R-squared) for BAI on PM
#full linear regression model

full_model <- lm(Accuracy ~ BAI + Age + Gender1, data = PM)
# model without the predictor
reduced_model <- lm(Accuracy ~ Age + Gender1, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```

```{r}
## Anxiety and ERPs

#Effect sizes (partial R-squared) for TRAIT on PP
#full linear regression model
full_model <- lm(PP ~ STAIT + Age + Gender1, data = PM)
# model without the predictor
reduced_model <- lm(PP ~ Age + Gender1, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```


```{r}
#Effect sizes (partial R-squared) for BAI on PP
#full linear regression model

full_model <- lm(PP ~ BAI + Age + Gender1, data = PM)
# model without the predictor
reduced_model <- lm(PP ~ Age + Gender1, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```



```{r}
#Effect sizes (partial R-squared) for TRAIT on N300

#full linear regression model
full_model <- lm(N300 ~ STAIT + Age + Gender1, data = PM)
# model without the predictor
reduced_model <- lm(N300 ~ Age + Gender1, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```


```{r}
#Effect sizes (partial R-squared) for BAI on N300
#full linear regression model
full_model <- lm(N300 ~ BAI + Age + Gender1, data = PM)
# model without the predictor
reduced_model <- lm(N300 ~ Age + Gender1, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)
```


```{r}
#Effect sizes (partial R-squared) for STAIS on N300

#full linear regression model
full_model <- lm(N300 ~ STAIS + Age + Gender1, data = PM)
# model without the predictor
reduced_model <- lm(N300 ~ Age + Gender1, data = PM)
# R-squared for the full model
r_squared_full <- summary(full_model)$r.squared
# R-squared for the reduced model
r_squared_reduced <- summary(reduced_model)$r.squared
partial_r_squared <- r_squared_full - r_squared_reduced
print(partial_r_squared)

```



# Anxiety score info for descriptives
```{r}
# STAIT
low <- filter(PM, BAI <= 15)

high <- filter(PM, BAI > 26)

view(high)

```




